{ \fontfamily{ptm}\selectfont Catalyst Meta Acceleration Framework: The history and the gist of it }

### 2024-11-15 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, fixed

    Introduced in Lin et al. \cite{lin_universal_2015}\cite{lin_catalyst_2018} is a series of papers describing a concrete meta algorithm called Catalyst (It's called 4WD Catalyst for the non-convex extension in works by Paquette, Lin et al. \cite{paquette_catalyst_2018}). 
    The meta algorithm uses other first order algorithms to evaluate inexact proximal point method and then performs accelerated PPM based on the outputs of other algorithms, hence the umbrella term: ``meta algorithm''. 
    The innovations here are tracking and controlling the errors made in the inexact PPM using Nesterov's estimating sequence throughout and an algorithm called accelerated MISO-Prox by Lin. 
    Prior to this paper, it was an open question on the conditions required to accelerate incremental method such as stochastic gradient descent can be accelerated.

@@

\bibliographystyle{siam}
\bibliography{references/refs}
\newpage

>>>>

    Introduced in Lin et al. \cite{lin_universal_2015,lin_catalyst_2018} is a series of papers on a concrete meta algorithm called Catalyst (It's called 4WD Catalyst for the non-convex extension in works by Paquette, Lin et al. \cite{paquette_catalyst_2018}). 
    The meta algorithm uses other first order algorithms to evaluate inexact proximal point method and then performs accelerated PPM, therefore the umbrella term: ``meta''. 
    Major innovations include Tracking and controlling the errors made in the inexact PPM using Nesterov's estimating sequence throughout and an algorithm called accelerated MISO-Prox.  
    Prior to Lin's paper, it was an open question on the conditions required to accelerate incremental method such as stochastic gradient descent can be accelerated.

@@

\bibliographystyle{siam}
\bibliography{references/refs.bib}
\newpage
